\huge Tor's Usability for Censorship Circumvention

### 2016-04-06 pets2017-paper/pets2017-paper.tex
Miscellaneous tiny fixes.

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
since become an important censorship circumvention tool. It is now listed
as one of the ways that normal people use Tor \cite{whotor}.
We specifically examine its usability as a censorship circumvention tool,
an essential facet for adoption and use. We focus our analysis on the connection 
configuration interface of Tor Browser, as censorship circumvention requires 
correct transport configurations. We find that the Tor Browser 5.0.3. connection
configuration interface has a success rate of {\color {red} TODO}\% with the 
successful users having an average completion time of {\color {red} TODO} minutes. 
In this paper, we explore common challenges users faced during the configuration
process and redesign the interface to improve success rate to {\color {red} TODO}\% 
and average completion time to {\color {red} TODO} minutes.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

\section{Introduction}
Tor is primarily known as the most widely used anonymity tool today. 
For this reason, user studies on Tor have been solely about the usability of Tor as an
anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
``stopping points'' in Tor Browser, documenting points when people would get frustrated enough
to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
Since then, Tor has had a lot of updates. There have been been no published usability evaluations of
Tor Browser since the introduction of the 4.0 series, which introduced radical UI changes. 
Lee and Fifield \cite {uxsprint} ran a small pilot study testing the download, install, and user interface of Tor Browser. 
This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
5.1 and later. There has been no work done on Tor as a censorship circumvention tool.

Many features of Tor have not been evaluated through user
research --- such as advanced web tasks (e.g., accessing hidden services), the
configuration menu to connect to the Tor network, configuring automatic
updates, and identity/cookie management. Rather than selecting the features to
study in isolation, we decided to focus on an important use case of Tor browser: censorship circumvention. 
Internet censorship is pervasive across the world today \cite{faris2008measuring}. 
Although Tor was not designed to be a censorship circumvention tool, users started
using it as one, since Tor's role as a proxy to anonymize
people also worked to circumvent censorship. Now, circumventing censorship is a
common use case for Tor, and current censorship circumvention methods are
incorporated into Tor, making it a viable censorship circumvention tool even in the face
of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason \cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool.

@@

\subsection{The Current Configuration Interface} 
The Tor Browser provides a configuration interface to guide users through setting up 
their connection. While most can connect to Tor using the
dialog's default settings, users in certain censorship environments must
make use of additional settings, such as bridges, proxies, or both. As bridges and proxies can be configured independently or together, there are
four main ways to set up a connection:

@@

The interface asks a series of questions to determine which of these configuration states a user requires. The first decision that a user needs to make is if they should connect directly to the Tor network or go through the process of  configuring a bridge and a proxy. The interface asks users questions along the way throughout the configuration to help guide their process on what components they would need to configure. For a successful configuration, users are required to know the following:

@@

An exploration of the problems with the existing Tor Browser 
configuration interface through user observation and interviews can be 
found in section {\color{red} TODO}. A heuristic evaluation of the existing interfaceand new interface is in section {\color{red} TODO}. We empirically show 
that the redesigned interface improves completion rate, reduces time to completion, 
and provides a safe path for at-risk users in section {\color{red} TODO}.

@@

\subsubsection{Recruitment}
Using established best practices from the field of user experience research
(\cite{howmanyusers}), we recruited 5 participants for each censorship environment.
We pre-screened our participants for diversity of gender, age, technical expertise,
and familiarity with Tor in each simluated censorship environment.

We recruited our users from Craigslist. The recruitment text can be found in 
Appendix \ref{qualitative-recruitment}. The recruitment posting contained a 
SurveyGizmo online survey that collected information about our participants.
The complete prescreening survey can be found in Appendix \ref{qualitative-prescreening}.

@@

The 1-hour, single-participant procedure begins when a participant enters a small 
room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, 
Chrome, and VLC (for screen recording). A participant is firstly informed of 
the risks of the study and consenting to data collection. If they consent, the 
experiment begins. A researcher informs the participant that they are in a
simulated censorship environment, where some websites and services are blocked. 
For the full script of what participants have heard, see Appendix \ref{qualitative-script}. We
instruct them to visit a sample blocked website and a sample non-blocked website on a
non-Tor browser of their choice to illustrate the situation.

@@

After users completed the browsing tasks or have spent the rest of the time
trying to configure Tor Browser, we interviewed participants about their experience.
We performed a live transcription of the interview to avoid recording voices, which is
considered personally identifying information. 
We asked three standard questions asking about their general experience, 
confusing interface features, and soliciting feedback for improvements. We followed up
with specific questions we had for a particular participant from observing their screen. 
This was to verify any hypothesis we had about the participant (i.e. ``they didn't know what to do on window 3'').  
After their interview, participants were informed that the experiment was over and 
given their payment of \$30.

\subsection{Results} 
In this section, we discuss problems encountered by our participants at each step of the configuration process and solutions to those problems. We conclude with our goals for improving the configuration interface. Because of the small sample size of qualitative studies, we can only state that these are problems that participants can encounter when configuring. We confirm the statistical significance of some of the problems in our quantitative study (section ~\ref {sec:quantitative}. All quotes are paraphrased from live transcriptions of participant interviews.\\

@@

\noindent P14:\textit{``The words were confusing. I don't really understand computers. I don't know what configure means in this setting. Hmm, is it going to crash? When you see connect, you want to click it because you really want it to connect..''} 
\end{quotation}

@@

\subsubsection{Bridge Configuration} 
When a participant chooses to configure their connection, their next step is to determine whether they need to configure a bridge, and to configure one if necessary. Answering yes to ``Does your Internet Service Provider (ISP) block of otherwise censor connections to the Tor Network'' directs to a bridge configuration screen, whereas answering no skips that screen. We observed that multiple participants struggled with the technical language on the screen, and ultimately decided to try trial and error. Most participants with the default option to not configure a bridge.

@@

None of our censorship environments required our participants to configure a proxy for a successful connection. And upon the first attempt at configuration, most chose the default value of not configuring a proxy.  However, the most common reason for of failing to connect was that participants spent time configuring a proxy when they needed to adjust  bridge settings instead. Currently, no information was given upon failing to connect, which caused our participants to draw their own (incorrect) conclusions after a failed connection. Since the interface passively re-displayed a proxy-related window seen after an attempted connection regardless of the error, many participants were convinced that they needed a proxy to connect to the Tor network.

@@

As a technical artifact of how the progress bar is implemented, the progress bar remains empty on subsequent attempts to connect to the Tor Network until the percent progress supersedes the last displayed progress value (i.e. a participant who saw 30\% progress on their first attempt would see 0\% progress in the progress bar until subsequent attempts got at least 40\% progress). The negative feedback of a 0\% progress bar would cause users to assume that their subsequent attempts were wrong, even if they were correct. 
\begin{quotation}
\noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, of if it was just slow.''}
\end{quotation}

@@

%\begin{quotation}
%\noindent{\bfseries P15}:\textit{``Give this to a couple of people who know how to do this. They can feel elite... they only want the elite to use some computer things..''} \\
%\noindent{\bfseries P13}:\textit{``I don't remember what I did. I figured it out? What? <laughs> Oh man, that's crazy..''}\\
%\noindent{\bfseries P11}:\textit{``Is this question (does your ISP censor your Internet connection) really necessary? I just selected that I have a censored connection, why do they ask me again?''}
%\end{quotation}

@@

Tor Browser 5.0.3. configuration interface does not adequately meet our heuristic evaluation criteria from Section ~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design. The configuration used for a connection is not visible to the users before they connect or while they are connecting, full control but little guidance through the configuration process confuse users, error messages do not express errors in plain language of offers solutions, the text was too technical for an average user to understand, and the interface has room be simplified visually.

@@

The redesigned interface maintains the approach taken by the deployed interface of asking the users about their situation, which is in the spirit of the deployed interface. The designed interface conservatively interacts with users by automating only safe configuration processes and still allowing users to have control over configuring all interacting network components. The design requires more maintenance because of the explicit advice given on which order to select bridges and advice on error messages, which may changes as the censorship environments change. For additional changes that can be made and alternate approaches for interacting with the user, see Section ~\ref{sec:discussion}.

@@

\subsubsection{Setup}
For consistency, we simulated the same three censorship environments from 
our qualitative user study. Details of the mild, intermediate, and advanced 
censorship environments and what configurations are necessary for a 
successful connection can be found in Section \ref{sec:setup}.

\subsubsection{Recruitment}
We recruited 20 users for each censorship environment
and interface combination, resulting in a total of 120 users. This decision 
was due to both data analysis considerations (large enough to have good effect size, 
with a minimum of 20 to be able to assume normal distributions) and funding
limitations.

We recruited half of our users from Craigslist, and half of our participants from 
the Xlab participant pool. It is standard for Xlab experiments to be run with Xlab
participants, who have been verified of their identity and have good attendance
rate. Although Xlab participants are not limited to UC Berkeley students and staff,
a majority of the participants are from campus. For this reason, we chose to recruit 
half of our participants from Craigslist to ensure a diverse set of participants. 
The recruitment text can be found in Appendix \ref{quantitative-recruitment}.

@@

The 1-hour, multi-participant procedure begins when all participants are sitting at their
respective computers in Xlab. Each computer is equipped with an old or modified version
of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording). 
Participants are firstly informed of the risks of the study and consenting to data collection.  At
this time, participants are given the chance to leave the laboratory if they do not consent to 
the experiment conditions. When every participant left in the room has turned in their consent
form, the experiment formally begins. A researcher informs the participants that they are in a
simulated censorship environment, where some websites and services are blocked. 
For the full script of what participants have heard, see Appendix \ref{quantitative-script}. We
instruct them to visit a sample blocked website on a non-Tor browser of their choice to illustrate 
the situation.

@@

After instructions, researchers maintained minimal interactions with the participants, 
only answering logistical questions. Participants had an 
average of 40 minutes to complete their worksheet. 
The participants do not know the details of their censorship environment,
only that they are actively being censored. Participants needed to configure Tor Browser to 
circumvent the simulated censorship.

After users completed the browsing tasks, they take a short exit survey (Appendix \ref{quantitative-exit-survey})
collecting their demographics. All users were instructed to sit until the end of the experiment,
regardless of when they had completed their task. This was to ensure that others were not 
aware of when other participants had finished their tasks. After the 40 minutes were up, 
participants were officially informed that their time was up, and were given their payment of 
\$30.

@@

Graph: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
\item{success rate}
\item{time to success: distribution}
\item{time to success: cdf and cutoffs at 2 min, 10 min, 20 min?}  
\item{time spent on each screen}
\item{order pluggable transports were chosen}
\item{transitions between windows for all participants}
\end{itemize} 
}

@@

Ideally, we want users in censorship environments across the world to succeed in connecting to the Tor network in a couple of minutes. Currently, the deployed nor redesigned interface achieves this goal. Additional user studies that focus specifically on users in heavily censored environments, or increasing the amount of automation in the configuration process can yield to higher rates of success and faster time to success. We encourage future work to explore some of the non-conservative changes and alternative approaches that we were not able to test in these series of experiment, which are listed in Section \ref{sec:discussion}.

\section{Discussion} 
\label{sec:discussion}
If we had more concrete information on the number of high-risk users or users who need to configure a proxy, we would have made additional changes in the prototype. Since we lacked this information, the following changes did not make it into our prototype, but are worth discussing. Depending on the number of high-risk users or proxy-configuring users, these additional changes may be helpful: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
\item {\bfseries Tell people to click connect.} On the first screen, the user needs to decide to connect or configure. Although there is a description of what each option entails and when one may consider using that option, there are no instructions for the user on what to do. Ideally, we would people to click connect, and then try the manual configuration if a direct connection fails. We currently do not communicate this because may put some users at risk. However, it is believed that a majority of the users will succeed if they click connect on the first screen, and giving them instructions on what to do can lessen their cognitive load during the configuration process. 
\item{\bfseries Hide the proxy screen.} Don't give users the option to configure a proxy unless it has been detected that it would be necessary. The amount of people who use proxies is low, but then ... this would not give users control in the beginning of the configuration process. 
\item{\bfseries Help the at-risk users.} There are people who would benefit from, on the first attempt, connecting with a meek bridge or custom bridge, without trying a vanilla tor connection or the recommended bridge in the dialog. Currently, we guide these people to the correct decision, but after trying the default bridge first. Helping these users to make a connection safely without ever being logged as connecting to Tor would be a benefit, but might be a case of overfitting to these types of users. A majority of users should not use a meek bridge or custom bridge, so it would be unideal to lead all users to this decision.
\end{itemize}

@@

\section{Qualitative User Study Recruitment Posting} 
We are recruiting participants for an in-person research study at the University of California, Berkeley. You will need to come in to our lab and perform tasks on a computer for an hour or less. You will be compensated \$30 for participating. 
No special knowledge and no technical experience is required.

@@

To circumvent censorship successfully, you will need to set up Tor browser correctly and use it to get to Wikipedia. If you are able to reach the website, then you know that you have successfully circumvented censorship. Fill out the question on the worksheet. This isn’t intended to be hard, just write what you see. We want to just check you saw the website.

>>>>

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
since become an important censorship circumvention tool. It is now listed
as one of the ways that normal people use Tor~\cite{whotor}.
We specifically examine its usability as a censorship circumvention tool,
an essential facet for adoption and use. We focus our analysis on the connection 
configuration interface of Tor Browser, as censorship circumvention requires 
correct transport configurations. We find that the Tor Browser 5.0.3. connection
configuration interface has a success rate of {\color {red} TODO}\% with the 
successful users having an average completion time of {\color {red} TODO} minutes. 
In this paper, we explore common challenges users faced during the configuration
process and redesign the interface to improve success rate to {\color {red} TODO}\% 
and average completion time to {\color {red} TODO} minutes.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

\section{Introduction}
Tor is primarily known as the most widely used anonymity tool today. 
For this reason, user studies on Tor have been solely about the usability of Tor as an
anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
``stopping points'' in Tor Browser, documenting points when people would get frustrated enough
to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
Since then, Tor has had a lot of updates. There have been been no published usability evaluations of
Tor Browser since the introduction of the 4.0 series, which introduced radical UI changes. 
Lee and Fifield~\cite {uxsprint} ran a small pilot study testing the download, install, and user interface of Tor Browser. 
This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
5.1 and later. There has been no work done on Tor as a censorship circumvention tool.

Many features of Tor have not been evaluated through user
research --- such as advanced web tasks (e.g., accessing hidden services), the
configuration menu to connect to the Tor network, configuring automatic
updates, and identity/cookie management. Rather than selecting the features to
study in isolation, we decided to focus on an important use case of Tor browser: censorship circumvention. 
Internet censorship is pervasive across the world today~\cite{faris2008measuring}. 
Although Tor was not designed to be a censorship circumvention tool, users started
using it as one, since Tor's role as a proxy to anonymize
people also worked to circumvent censorship. Now, circumventing censorship is a
common use case for Tor, and current censorship circumvention methods are
incorporated into Tor, making it a viable censorship circumvention tool even in the face
of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason~\cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool.

@@

\subsection{The Current Configuration Interface} 
Tor Browser provides a configuration interface to guide users through setting up 
their connection. While most can connect to Tor using the
dialog's default settings, users in certain censorship environments must
make use of additional settings, such as bridges, proxies, or both. As bridges and proxies can be configured independently or together, there are
four main ways to set up a connection:

@@

The interface asks a series of questions to determine which of these configuration states a user requires. The first decision that a user needs to make is if they should connect directly to the Tor network or go through the process of  configuring a bridge and a proxy. The interface asks users questions along the way throughout the configuration to help guide their process on what components they would need to configure. For a successful configuration, users are required to know (or find out) the following:

@@

An exploration of the problems with the existing Tor Browser 
configuration interface through user observation and interviews can be 
found in Section~{\color{red} TODO}. A heuristic evaluation of the existing interface and new interface is in Section~{\color{red} TODO}. We empirically show 
that the redesigned interface improves completion rate, reduces time to completion, 
and provides a safe path for at-risk users in Section~{\color{red} TODO}.

@@

\subsubsection{Recruitment}
Using established best practices from the field of user experience research~\cite{howmanyusers},
we recruited 5 participants for each censorship environment.
We pre-screened our participants for diversity of gender, age, technical expertise,
and familiarity with Tor in each simluated censorship environment.

We recruited our users from Craigslist. The recruitment text can be found in 
Appendix~\ref{qualitative-recruitment}. The recruitment posting contained a 
SurveyGizmo online survey that collected information about our participants.
The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.

@@

The one-hour, single-participant procedure begins when a participant enters a small 
room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, 
Chrome, and VLC (for screen recording). A participant is firstly informed of 
the risks of the study and consenting to data collection. If they consent, the 
experiment begins. A researcher informs the participant that they are in a
simulated censorship environment, where some websites and services are blocked. 
For the full script of what participants have heard, see Appendix~\ref{qualitative-script}. We
instruct them to visit a sample blocked website and a sample non-blocked website on a
non-Tor browser of their choice to illustrate the situation.

@@

After users completed the browsing tasks or have spent the rest of the time
trying to configure Tor Browser, we interviewed participants about their experience.
We performed a live transcription of the interview to avoid recording voices, which is
considered personally identifying information. 
We asked three standard questions asking about their general experience, 
confusing interface features, and soliciting feedback for improvements. We followed up
with specific questions we had for a particular participant from observing their screen. 
This was to verify any hypothesis we had about the participant (i.e. ``they didn't know what to do on window~3'').  
After their interview, participants were informed that the experiment was over and 
given their payment of~\$30.

\subsection{Results} 
In this section, we discuss problems encountered by our participants at each step of the configuration process and solutions to those problems. We conclude with our goals for improving the configuration interface. Because of the small sample size of qualitative studies, we can only state that these are problems that participants can encounter when configuring. We confirm the statistical significance of some of the problems in our quantitative study (Section~\ref{sec:quantitative}). All quotes are paraphrased from live transcriptions of participant interviews.\\

@@

\noindent P14:\textit{``The words were confusing. I don't really understand computers. I don't know what configure means in this setting. Hmm, is it going to crash? When you see connect, you want to click it because you really want it to connect.''} 
\end{quotation}

@@

\subsubsection{Bridge Configuration} 
When a participant chooses to configure their connection, their next step is to determine whether they need to configure a bridge, and to configure one if necessary. Answering yes to ``Does your Internet Service Provider (ISP) block or otherwise censor connections to the Tor Network'' directs to a bridge configuration screen, whereas answering no skips that screen. We observed that multiple participants struggled with the technical language on the screen, and ultimately decided to try trial and error. Most participants with the default option to not configure a bridge.

@@

None of our censorship environments required our participants to configure a proxy for a successful connection. And upon the first attempt at configuration, most chose the default value of not configuring a proxy.  However, the most common reason for failing to connect was that participants spent time configuring a proxy when they needed to adjust  bridge settings instead. Currently, no information was given upon failing to connect, which caused our participants to draw their own (incorrect) conclusions after a failed connection. Since the interface passively re-displayed a proxy-related window seen after an attempted connection regardless of the error, many participants were convinced that they needed a proxy to connect to the Tor network.

@@

As a technical artifact of how the progress bar is implemented, the progress bar remains empty on subsequent attempts to connect to the Tor Network until the percent progress supersedes the last displayed progress value (i.e. a participant who saw 30\% progress on their first attempt would see 0\% progress in the progress bar until subsequent attempts got at least 40\% progress). The negative feedback of a 0\% progress bar would cause users to assume that their subsequent attempts were wrong, even if they were correct. 
\begin{quotation}
\noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.''}
\end{quotation}

@@

%\begin{quotation}
%\noindent{\bfseries P15}:\textit{``Give this to a couple of people who know how to do this. They can feel elite\ldots they only want the elite to use some computer things..''} \\
%\noindent{\bfseries P13}:\textit{``I don't remember what I did. I figured it out? What? <laughs> Oh man, that's crazy..''}\\
%\noindent{\bfseries P11}:\textit{``Is this question (does your ISP censor your Internet connection) really necessary? I just selected that I have a censored connection, why do they ask me again?''}
%\end{quotation}

@@

Tor Browser 5.0.3. configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design. The configuration used for a connection is not visible to the users before they connect or while they are connecting, full control but little guidance through the configuration process confuse users, error messages do not express errors in plain language nor offer solutions, the text was too technical for an average user to understand, and the interface has room to be simplified visually.

@@

The redesigned interface maintains the approach taken by the deployed interface of asking the users about their situation, which is in the spirit of the deployed interface. The designed interface conservatively interacts with users by automating only safe configuration processes and still allowing users to have control over configuring all interacting network components. The design requires more maintenance because of the explicit advice given on which order to select bridges and advice on error messages, which may change as the censorship environments change. For additional changes that can be made and alternate approaches for interacting with the user, see Section~\ref{sec:discussion}.

@@

\subsubsection{Setup}
For consistency, we simulated the same three censorship environments from 
our qualitative user study. Details of the mild, intermediate, and advanced 
censorship environments and what configurations are necessary for a 
successful connection can be found in Section~\ref{sec:setup}.

\subsubsection{Recruitment}
We recruited 20 users for each censorship environment
and interface combination, resulting in a total of 120 users. This decision 
was due to both data analysis considerations (large enough to have good effect size, 
with a minimum of 20 to be able to assume normal distributions) and
available funding.

We recruited half of our users from Craigslist, and half of our participants from 
the Xlab participant pool. It is standard for Xlab experiments to be run with Xlab
participants, who have been verified of their identity and have good attendance
rate. Although Xlab participants are not limited to UC Berkeley students and staff,
a majority of the participants are from campus. For this reason, we chose to recruit 
half of our participants from Craigslist to ensure a diverse set of participants. 
The recruitment text can be found in Appendix~\ref{quantitative-recruitment}.

@@

The one-hour, multi-participant procedure begins when all participants are sitting at their
respective computers in Xlab. Each computer is equipped with an old or modified version
of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording). 
Participants are firstly informed of the risks of the study and consenting to data collection.  At
this time, participants are given the chance to leave the laboratory if they do not consent to 
the experiment conditions. When every participant left in the room has turned in their consent
form, the experiment formally begins. A researcher informs the participants that they are in a
simulated censorship environment, where some websites and services are blocked. 
For the full script of what participants have heard, see Appendix~\ref{quantitative-script}. We
instruct them to visit a sample blocked website on a non-Tor browser of their choice to illustrate 
the situation.

@@

After instructions, researchers maintained minimal interactions with the participants, 
only answering logistical questions. Participants had
40 minutes to complete their worksheet. 
The participants do not know the details of their censorship environment,
only that they are actively being censored. Participants needed to configure Tor Browser to 
circumvent the simulated censorship.

After users completed the browsing tasks, they take a short exit survey (Appendix~\ref{quantitative-exit-survey})
collecting their demographics. All users were instructed to sit until the end of the experiment,
regardless of when they had completed their task. This was to ensure that others were not 
aware of when other participants had finished their tasks. After the 40 minutes were up, 
participants were officially informed that their time was up, and were given their payment of 
\$30.

@@

Graph: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
\item{success rate}
\item{time spent on each screen}
\item{order pluggable transports were chosen}
\item{transitions between windows for all participants}
\end{itemize} 
}

@@

Ideally, we want users in censorship environments across the world to succeed in connecting to the Tor network in a couple of minutes. Currently, the deployed nor redesigned interface achieves this goal. Additional user studies that focus specifically on users in heavily censored environments, or increasing the amount of automation in the configuration process can yield to higher rates of success and faster time to success. We encourage future work to explore some of the non-conservative changes and alternative approaches that we were not able to test in these series of experiment, which are listed in Section~\ref{sec:discussion}.

\section{Discussion} 
\label{sec:discussion}
If we had more concrete information on the number of high-risk users or users who need to configure a proxy, we would have made additional changes in the prototype. Since we lacked this information, the following changes did not make it into our prototype, but are worth discussing. Depending on the number of high-risk users or proxy-configuring users, these additional changes may be helpful: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
\item {\bfseries Tell people to click connect.} On the first screen, the user needs to decide to connect or configure. Although there is a description of what each option entails and when one may consider using that option, there are no instructions for the user on what to do. Ideally, we would people to click connect, and then try the manual configuration if a direct connection fails. We currently do not communicate this because it may put some users at risk. However, it is believed that a majority of the users will succeed if they click connect on the first screen, and giving them instructions on what to do can lessen their cognitive load during the configuration process. 
\item{\bfseries Hide the proxy screen.} Don't give users the option to configure a proxy unless it has been detected that it would be necessary. The amount of people who use proxies is low, but then \ldots this would not give users control in the beginning of the configuration process. 
\item{\bfseries Help the at-risk users.} There are people who would benefit from, on the first attempt, connecting with a meek bridge or custom bridge, without trying a vanilla tor connection or the recommended bridge in the dialog. Currently, we guide these people to the correct decision, but after trying the default bridge first. Helping these users to make a connection safely without ever being logged as connecting to Tor would be a benefit, but might be a case of overfitting to these types of users. A majority of users should not use a meek bridge or custom bridge, so it would be unideal to lead all users to this decision.
\end{itemize}

@@

\section{Qualitative User Study Recruitment Posting} 
\label{qualitative-recruitment}
We are recruiting participants for an in-person research study at the University of California, Berkeley. You will need to come in to our lab and perform tasks on a computer for an hour or less. You will be compensated \$30 for participating. 
No special knowledge and no technical experience is required.

@@

To circumvent censorship successfully, you will need to set up Tor browser correctly and use it to get to Wikipedia. If you are able to reach the website, then you know that you have successfully circumvented censorship. Fill out the question on the worksheet. This isn't intended to be hard, just write what you see. We want to just check you saw the website.
